Real-Life Algebraic File Synchronization

### 2015-10-31 2015/paper.tex
Reduced the types of relationships in pairs of commands

\newcommand{\setv}{\mathcal{V}}
\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
\newcommand{\setf}{\setvx{F}}
\newcommand{\setd}{\setvx{D}}
\newcommand{\setb}{\setvx{\empt}}
\newcommand{\setp}{\mathcal{P}}
\newcommand{\empt}{\bot}
\newcommand{\parent}{\mathtt{parent}}
\newcommand{\FS}{\Phi} % {\mathrm{FS}}
\newcommand{\GS}{\Xi} % another filesystem

\newcommand{\cbrk}{\mathtt{break}}
\newcommand{\cbb}{\overrightarrow{\empt\empt}}
\newcommand{\cbf}{\overrightarrow{\empt{F}}}
\newcommand{\cbd}{\overrightarrow{\empt{D}}}
\newcommand{\cfb}{\overrightarrow{F\empt}}
\newcommand{\cff}{\overrightarrow{FF}}
\newcommand{\cfd}{\overrightarrow{FD}}
\newcommand{\cdb}{\overrightarrow{D\empt}}
\newcommand{\cdf}{\overrightarrow{DF}}
\newcommand{\cdd}{\overrightarrow{DD}}
\newcommand{\cxy}{\overrightarrow{XY}}
\newcommand{\czw}{\overrightarrow{ZW}}

@@

We model a filesystem using a function $\FS$ with a set of paths $\setp$ as its domain,
and a set of possible contents $\setv$ as its codomain:
\[ \FS : \setp \rightarrow \setv \] 
In our model, $\setp$ contains all possible paths, and $\setv$ contains a special
element, $\empt$, which is the value of $FS$ at paths where there are no files
or directories.
We consider the contents of files, as well as any meta-information on files
and directories (e.g. permissions or flags) part of the values in $\setv$.

@@

In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
of $\setd$. $V$ is usually a value from $\setv$ and $p$ is a path in $\setp$.

@@

We therefore propose to have a command for each pair of types.
For want of a better system, we will simply name our commands by concatenating
two of $D$, $F$ and $\empt$ with an arrow, where the left sign notes the type of value
in the filesystem before the command is applied, and the right sign notes the type
afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.

@@

Pairs of commands in general will have the form
\[ \cxy(p,V_Y) \czw(q,V_W) \]
where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
(although commands where $Y=\empt$ or $W=\empt$ do not require a value).

Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
a set of axioms in a sound and complete algebra we at times needed to take into account
the relationship between the paths of the commands in the pair, $p$ and $q$.
As the relationship between the paths determine how the commands affect the filesystem
and its tree property, 
and again in line with the aim of providing as much information as possible for the algebra,
we encoded this relationship in the pair of commands. The possible relationships we
need to take into account are as follows.

\begin{itemize}
\item $p=q$.
\item $\parent(p)=q$ and $\parent(q)=p$. We know that 
\item Only child
\item separate
\end{itemize}

>>>>

\newcommand{\setv}{\mathcal{V}}
\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
\newcommand{\setf}{\setvx{F}}
\newcommand{\setd}{\setvx{D}}
\newcommand{\setb}{\setvx{\empt}}
\newcommand{\setp}{\mathcal{P}}
\newcommand{\empt}{\bot}
\newcommand{\parent}{\mathtt{parent}}
\newcommand{\FS}{\Phi} % {\mathrm{FS}}
\newcommand{\GS}{\Xi} % another filesystem
\newcommand{\pp}{\hat{p}} % parent path
\newcommand{\np}{\mathrel{\ooalign{$p$\cr\hidewidth\hbox{$-$}\cr}}} % path not related to p

\newcommand{\cbrk}{\mathtt{break}}
\newcommand{\fscommand}[2]{{#1#2}}
\newcommand{\cbb}{\fscommand{\empt\empt}}
\newcommand{\cbf}{\fscommand{\empt{F}}}
\newcommand{\cbd}{\fscommand{\empt{D}}}
\newcommand{\cfb}{\fscommand{F\empt}}
\newcommand{\cff}{\fscommand{FF}}
\newcommand{\cfd}{\fscommand{FD}}
\newcommand{\cdb}{\fscommand{D\empt}}
\newcommand{\cdf}{\fscommand{DF}}
\newcommand{\cdd}{\fscommand{DD}}
\newcommand{\cxy}{\fscommand{XY}}
\newcommand{\czw}{\fscommand{ZW}}

@@

We model a filesystem using a function $\FS$ with a set of paths $\setp$ as its domain,
and a set of possible contents $\setv$ as its codomain:
\[ \FS : \setp \rightarrow \setv \] 
In our model, $\setp$ contains all possible paths, and $\setv$ contains a special
element, $\empt$, which is the value of $\FS$ at paths where there are no files
or directories.
We consider the contents of files, as well as any meta-information of files
and directories (e.g. permissions or flags) part of the values in $\setv$.

@@

In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
of $\setd$. $V$ is usually a value from $\setv$ and $p$ and $q$ are paths in $\setp$.

@@

We therefore propose to have a command for each pair of types.
For want of a better system, we will simply name our commands by concatenating
two of $\fscommand{D}{}$, $\fscommand{F}{}$ and $\fscommand{\empt}{}$, 
where the left sign notes the type of value
in the filesystem before the command is applied, and the right sign notes the type
afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.

@@

Pairs of commands in general will have the form
\[ \cxy(p,V_Y); \czw(q,V_W) \]
where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
(although commands where $Y=\empt$ or $W=\empt$ do not require a value).

Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
a set of axioms in a sound and complete algebra we at times needed to take into account
the relationship between the paths of the commands in the pair, $p$ and $q$.
As the relationship between the paths determine how the commands affect the filesystem
and its tree property, 
and again in line with the aim of providing as much information as possible for the algebra,
we encode this relationship in the pair of commands. The possible relationships we
consider are as follows.

\begin{itemize}
\item $p=q$. If the two commands affect the same path, the pair of commands
will clearly behave differently than if the paths are different.
\item Separate paths, that is, $\parent(p)\neq q$ and $\parent(q)\neq p$. If the paths
are not directly related, then modifying the filesystem at one path is not going
to affect the outcome of the command on the other path.
The two commands will therefore commute and the pair will be reversible.
\item Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
Some of these command pairs will not be reversible.
For example, $\cbd(\parent(p),D);\cbf(p,F)$ will work on some filesystems,
while $\cbf(p,F);\cbd(\parent(p),D)$ will break all filesystems.
\end{itemize}

One may think that we may be able to specify more about the reversibility
or possible simplification of a pair of commands in the last group if we also
knew whether the child path $p$ was the only (non-empty) child of its parent.
However, it is easy to see that encoding this information in a pair
is not going to enrich our algebra as, for example,
the behaviour of a hypothetical $\cfb(p_{\mathrm{only\ child}}); \cdb(\parent(p))$
is exactly the same as that of the more generic
$\cfb(p); \cdb(\parent(p))$. The former will break any filesystem in which
$p$ is not the only child as it violates its preconditions, but so will
the generic pair.

In summary, if we adopt the notation $\pp := \parent(p)$ and use $\np$ for a path not directly related to $p$,
then we have pairs of commands
of the following forms:
\begin{align*}
\cxy(p,V_Y)&; \czw(p,V_W) \\
\cxy(p,V_Y)&; \czw(\np,V_W) \\
\cxy(p,V_Y)&; \czw(\pp,V_W) \\
\cxy(\pp,V_Y)&; \czw(p,V_W)
\end{align*}
